Differential chemotaxis with competition as a mapping mechanism in the brain

### 2023-09-15 paper/draft1/zerodraft.tex
Adds an archive of draft1, to refer back to.

% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_wt_fig3.json
\begin{figure}
\includegraphics[width=\linewidth]{./images/j4_eE_G_wt_fig3_exit_true.png}
\caption{By tuning the tectal ligand expression (replacing Eq.\,\ref{e:tecligexp} with
 Eq.\,\ref{e:tecligexp2}), the pure gradient-following model can achieve a
 successful layout in which the axons are arranged evenly across the full
 tectum. At the centre of the tectum, where neither retinal receptor
 expression nor tectal ligand expression is high, the ordering is weaker than
 towards the edge. \textbf{A} Axon branches \textbf{B} axon
 centroids \textbf{C} The pattern metric $\eta$ is zero, as it was in
 Fig.\,\ref{f:G}F and $\epsilon$ approaches a much lower value as $t \to \infty.}
\label{f:G0}
\end{figure}

>>>>

% ./build/sim/agent/agent1 configs/simpler/m_eE_G.json  configs/simpler/e_wt_fig3.json
\begin{figure}
\includegraphics[width=\linewidth]{./images/j4_eE_G_wt_fig3_exit_true.png}
\caption{By tuning the tectal ligand expression (replacing Eq.\,\ref{e:tecligexp} with
 Eq.\,\ref{e:tecligexp2}), the pure gradient-following model can achieve a
 successful layout in which the axons are arranged evenly across the full
 tectum. At the centre of the tectum, where neither retinal receptor
 expression nor tectal ligand expression is high, the ordering is weaker than
 towards the edge. \textbf{A} Axon branches \textbf{B} axon
 centroids \textbf{C} The pattern metric $\eta$ is zero, as it was in
 Fig.\,\ref{f:G}F and $\epsilon$ approaches a much lower value as $t \to \infty$.}
\label{f:G0}
\end{figure}
